\chapter{Performance Analysis}
%high prio
Performance experiments:

%statistical restrictions, show you are aware of restricitons. what you have tested only once, twice, etc..

\section{Startup time}
Startup experience

\section{GUI Responose Time}
Latency during first hour, after first hour
What does it say about the design?

\section{Content Discovery Performance}
First discovered content, latency, cdf

\section{Search Performance}
Search results response time, latency, cdf





\section{Typical System Load}
y: cpu usage
x: time 0-3 uur

Graph showing cpu and memory consumption from fresh install to an hour idling. 0 tunnels.

Graph showing cpu and memory consumption with max. 10 tunnels after an hour idling.

Graph showing cpu and memory consumption during single download after an hour idling. 0 tunnels.

Graph showing cpu and memory consumption during streaming HD video after an hour idling. 0 tunnels.



stacking of cost, turn all off, turn on one by one or peel off some functionality, look at resulting workload / impact on performace / give relative cost of component

\section{CProfiler Analysis}
Graph showing wall clock time spend on functions running 10 minutes during first half hour with max. 10 tunnels.
flame graph

\section{Test Suite Performance}
Graph showing total run time and average run time per test.

Code coverage?

\section{Multi-chain Scalability Experiment}
Multichain record creation cost
Graph showing scalability or lack thereof of the multi-chain record creation cost.


\section{Phone-to-Phone new content discover time}



\section{Transfer time of app}



\section{DAS5 1 to 1000000} 


