Introduction

Modern media and news distribution is shifting from traditional media to social media.
Modern media production and information distribution is shifting from traditional outlets.
Also media consumption is shifting from traditional outlets to digital and mobile devices.
from con-sumer to pro-sumer.
Niet gebonden aan expert opinion / editorial, maar aan eigen mening zonder professionele studio / news desk / kantoor; maar juist mobile eye-witness; direct van individu naar massa!

%What advantages does a smart phone have compared to a laptop and desktop?
Given this context mobile devices are increasingly important and smart-phone in particular.
A smart-phone has the unique property of being a ubiquitous device that is highly mobile and extremely connectible.
Most smart-phones even have one or more cameras to produce multi-media content that can be shared immediately from the device.
Finally the entire world has a smart-phone.
Even or especially areas without tradition infrastructure they are ubiquitous.

In crisis situations, like natural disaster or unrest, the smart-phone becomes particularly important, exactly for the earlier mentioned properties, as under such conditions utilizing centralized infrastructure is undesired (censorship) or physically impossible.
Decentralized can work in these situations.
Censorsihp and large scale monitoring is difficult in decentralized networks.
Refereren aan article Johan 2011 voorbeeld.


Tribler is a fully decentralized video-on-demand platform.
It is autonomous, attack-resilient and self-organizing.
It uses network overlays called communities to offer features like keyword search and managing contributions to channels for discover-ability of content.
It offers privacy through layered encrypted tunnels similar to the TOR network.

So far Tribler only supports desktop and server versions of Linux, Mac and Windows.
The necessity of moving to mobile devices calls for Tribler functionality to be enabled to run on these resource limited devices.
In this thesis the first prototype is presented that has all Tribler functionality fully enabled on mobile devices.
The prototype is build for Android OS since Android dominates the smart-phone market.
% maybe geographical spread of Android?


The research question is: how feasible is it to run all Tribler functionality on mobile devices? % to defeat or mitigate large scale monitoring and censorship?
Secondary question is: using the unique properties of mobile devices, what features can be added or enhanced?


bijdrage: faciliterend voor future research, nuttig. Tribler features + phone benefits
feasibility, opportunities enables future research, fully geared to mobile
het onderzoek staat nu toe om geverifieerd worden op beoogde use-cases.



Chapter 2 describes .....